---
title: "Homework 1"
author: chenxin zhang
output: github_document
---

This is my solution to HW1. 

```{r}
library(tidyverse)
```

## problem 1

Create a data frame with the specified elements:

```{r}
prob1_df =
  tibble(
  samp = rnorm(10),
  samp_gt_0 = samp > 0,
  char_vec = c("a", "b", "c", "d", "e", "f", "g", "h", "i","j"),
  factor_vec = factor(c("low", "low", "low", "mod", "mod", "mod", "mod", "high", "high", "high"))
    )
```

Take the mean of each variable in my data frame.

```{r}
mean(pull(prob1_df, samp))
mean(pull(prob1_df, samp_gt_0))
mean(pull(prob1_df, char_vec))
mean(pull(prob1_df, factor_vec))
```
I can take the mean of numbers and logical but not character or factor.

```{r}
as.numeric(pull(prob1_df, samp))
as.numeric(pull(prob1_df, samp_gt_0))
as.numeric(pull(prob1_df, char_vec))
as.numeric(pull(prob1_df, factor_vec))
```

```{r}
as.numeric(pull(prob1_df, samp_gt_0))*pull(prob1_df, samp)
```


## problem 2
#### 1. A short description of the penguins dataset 

```{r}
data("penguins", package = "palmerpenguins")
```

* The data in this dataset, including `r names(penguins)`.
  * The species are `r levels(pull(penguins, species))`
  * The island are `r levels(pull(penguins, island))`
  * The bill length range is `r range(pull(penguins, bill_length_mm), na.rm = TRUE )`
  * The bill depth range is `r range(pull(penguins, bill_depth_mm), na.rm = TRUE )`
  * The flipper length range is `r range(pull(penguins, flipper_length_mm), na.rm = TRUE )`
  * The body mass range is `r range(pull(penguins, body_mass_g), na.rm = TRUE )`
  * The sex contains `r levels(pull(penguins, sex))`
  * The year range is `r range(pull(penguins, year), na.rm = TRUE )`

* The size of the dataset is `r nrow(penguins)` rows and `r ncol(penguins)` columns.

* The mean flipper length is `r mean(pull(penguins, flipper_length_mm), na.rm = TRUE)`


#### 2. Scatterplot of flipper_length vs. bill_length

```{r}
ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) + geom_point()
```


```{r}
ggsave("scatter_plot.pdf", height = 10, width = 10)
```








